---
title: "Purrr solution"
author: "Callum"
date: "21/04/2022"
output:
  html_document: default
  pdf_document: default
---
This script builds on synergy_script_with_shuffled_data to increase efficiency and 
to incorporate different forms of RQA using functional programming with purrr
Reading in the data
```{r}
library(tidyverse)
library(purrr)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(crqa)
library(tseriesChaos)
library(entropy)
library(plot3D)
library(lme4)
library(cowplot)
library(gridExtra)
library(reshape2)

#Choose how to import the data
#1: there are many files in the directory

#temp = list.files(pattern="*.csv")
#myfiles = lapply(temp, read.csv)
# there is now a list of dataframes called myfiles

#2: All the data is in a single file
Data <- read_csv("Anon Full Recurrence dataset2.csv")
Data$dyadtrial <- paste(Data$dyadname, Data$trial)
myfiles <- Data %>% split(.$dyadtrial)
##there is now a list of dataframes called myfiles
```
For an efficient solution we can define the functions that we are going to use in the analysis before running it them on all trials. Set the parameters for all recordings here
```{r}
#Set the arqa params for all trials here
arqa.map <- function(seq) {
  crqa(ts1 = seq, ts2 = seq, delay = 1, embed = 12, rescale = 0, 
       radius = .8, normalize = 0, mindiagline = 2, minvertline = 2,
       tw = 1) 
  # setting tw to 1 removes Line of Identity/Incidence for auto-recurrence analysis
}

#Creating two arqa.map functions allow you to set different parameters for the 
#synergy and auto recurrence calculations 
arqa.map2 <- function(seq) {
  crqa(ts1 = seq, ts2 = seq, delay = 1, embed = 12, rescale = 0, 
       radius = .8, normalize = 0, mindiagline = 2, minvertline = 2,
       tw = 1) 
  # setting tw to 1 removes Line of Identity/Incidence for auto-recurrence analysis
}

#Set the crqa params for all trials here
crqa.map <- function(seq1, seq2) {
  crqa(ts1 = seq1, ts2 = seq2, delay = 0.5, embed = 1, rescale = 0, 
       radius = 0.1, normalize = 1, mindiagline = 2, minvertline = 2)
}

##A function that plots the RP for any rqa results passed to it
param = list(unit = 3, labelx = "", labely = "", cols = "dark green",
             pcex =.01, pch = 19, labax = NA, labay = NA, las = 1)


RQAplot <- function(x){
  x.RP <- x$RP
  plotRP(x.RP,param)
  plot = recordPlot()##Base R plots are not automatically stored in a list, recordPlot() allows us to store them
}
```

We can define all of the analyses that we want in one function before mapping it over all trials 
and binding the trials into a dataframe using purrr's map_dfr function
```{r}
analysis <- function(x) {
  df = melt(x, id.vars = c("rownumber", "dyad", "trial", "NameA",
                                         "NameB", "dyadname", "condition",
                                         "PatternA", "PatternB", "PatternANum",
                                         "PatternBNum", "CounterbalancingGroup",
                                         "itiPartnerA", "itiPartnerB", "dyadtrial"),
                          variable.names="joint_clapping")
  synergy <- df$value
  sorted_synergy <- sort(synergy, na.last = TRUE)
  
  ici <- vector()
  for(i in 1:length(sorted_synergy - 1)){
    ici[i] <- sorted_synergy[i + 1] - sorted_synergy[i]
  }
  
  syn.arqa <- arqa.map(ici)
  RQAplot(syn.arqa) ##We can just plot the RPs as they are created like this but it's not a
  ##useful way to present them
  
  iciA <- sort(df$itiPartnerA[!duplicated(df$itiPartnerA)])
  iciB <- sort(df$itiPartnerB[!duplicated(df$itiPartnerB)])
  
  partA.arqa <- arqa.map2(iciA)
  RQAplot(partA.arqa)

  partB.arqa <- arqa.map2(iciB)
  RQAplot(partB.arqa)
  
  iciAreplace <- iciA[is.na(iciA)] <- 0 #should we replace the NAs with 0 so that the         clapping
  #sequences are the same length for crqa?
  iciBreplace <- iciB[is.na(iciB)] <- 0
 
  synch.crqa <- crqa.map(iciAreplace, iciBreplace)
  #RQAplot(synch.crqa) ## Not sure how to set the parameters for crqa currently they return   NA rr values,
  ##Don't uncomment it will stop the function atm
  
  new_df <- data.frame(sorted_synergy,
             ici,syn.arqa$RR,syn.arqa$DET,
             synch.crqa$RR,synch.crqa$DET,
             partA.arqa$RR, partA.arqa$DET,
             partB.arqa$RR, partB.arqa$DET
             )
  colnames(new_df) <- c("synergy","ici",
                    "syn_arqa.RR", "syn_arqa.DET", 
                    "synch_crqa.RR","synch_crqa.DET",
                    "Aarqa.RR",
                    "Aarqa.DET", "Barqa.RR", "Barqa.DET"
                    )
  cbind(x, new_df)
  }

##creating a new Data frame with all of the desired analyses results added into new columns
new_data <- purrr::map_dfr(myfiles, analysis)
new_data$Patterns <- paste(new_data$PatternANum, new_data$PatternBNum)

```

```{r}
ggplot(new_data, aes(condition, syn_arqa.RR, fill = condition)) + geom_violin() +
  xlab("complexity condition") +
  ylab("Synergy Recurrence Rate") +
  theme_bw()
```
```{r}
ggplot(new_data, aes(condition, Aarqa.RR, fill = condition)) + geom_violin() +
  xlab("complexity condition") +
  ylab("ARQA Recurrence Rate") +
  theme_bw()
```
```{r}
ggplot(new_data, aes(condition, syn_arqa.DET, fill = condition)) + geom_violin() +
  xlab("complexity condition") +
  ylab("Synergy DET") +
  theme_bw()
```
```{r}
ggplot(new_data, aes(condition, Aarqa.DET, fill = condition)) + geom_violin() +
  xlab("complexity condition") +
  ylab("ARQA DET") +
  theme_bw()
```
```{r}
ggplot(new_data, aes(Patterns, syn_arqa.RR, fill = condition)) + geom_violin() +
  xlab("Pattern combination") +
  ylab("synergy Recurrence Rate") +
  theme_bw()
```
```{r}
ggplot(new_data, aes(Patterns, Aarqa.RR, fill = condition)) + geom_violin() +
  xlab("Pattern combination") +
  ylab("ARQA Recurrence Rate") +
  theme_bw()
```
```{r}
ggplot(new_data, aes(Patterns, syn_arqa.DET, fill = condition)) + geom_violin() +
  xlab("Pattern combination") +
  ylab("synergy DET") +
  theme_bw()
```
```{r}
ggplot(new_data, aes(Patterns, Aarqa.DET, fill = condition)) + geom_violin() +
  xlab("Pattern combination") +
  ylab("ARQA DET") +
  theme_bw()
```

